\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-26 manuscript.tex
first commit to GitHub
final touch; submit to ECC

\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{dding_template}
\input{\template/preamble/preamble_conf.tex}

@@

% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
One of the common issues in using NNs as control compontnets is that the outputs of NNs are not predictable.
This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.

@@

To approximate the desired controller, an NN is utilized.
Even though DNNs have a higher approximation capability than SHLNNs \cite{Rolnick:2018aa}, here, an SHLNN is utilized for simplicity and low computational complexity.
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
    ,
\end{equation}
where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

@@

All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
The validity of the selected number of nodes were demonstrated through experiments 
The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% {\footnotesize
    \bibliographystyle{ieeetr}
    \bibliography{dding_template/refs}
% }

>>>>

\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_conf.tex}

@@

% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
One of the common issues in using NNs as control components is that the outputs of NNs are not predictable.
This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control components from NNs.

@@

To approximate the desired controller, an NN is utilized.
Even though DNNs have a higher approximation capability than SHLNNs \cite{Rolnick:2018aa}, here, an SHLNN is utilized for simplicity and low computational complexity.
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
    ,
\end{equation}
where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denotes the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

@@

All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
The validity of the selected number of nodes were demonstrated through experiments.
The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% {\footnotesize
    \bibliographystyle{ieeetr}
    \bibliography{\template/refs}
% }
